\documentclass[12 pt, a4paper, notitlepage]{report}

%bibliography
\usepackage[a4paper,width=150mm,top=40mm,bottom=25mm]{geometry}
\usepackage[utf8x]{inputenc}
\DeclareUnicodeCharacter{8239}{okay}
\usepackage[scaled]{helvet}
% \usepackage{underscore}

\usepackage{setspace}
\usepackage{graphicx}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\leftmark}
\fancyfoot{}
\rfoot{\thepage}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{lscape}
\usepackage{subfiles}
\graphicspath{{figure/}{../figure/}}

%use single spacing after period
\frenchspacing

\usepackage[round]{natbib}
%\usepackage[natbib=true, style=authoryear]{biblatex}
%\bibliography{references/chapter2_ref}
%\bibliographystyle{abbrvnat}
\usepackage{chapterbib}


\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{pdflscape}
\usepackage{enumerate}
\usepackage[singlelinecheck=false]{caption}
\usepackage{longtable}
%for cv
% \usepackage{multicol}
% \usepackage{titlesec}
% \usepackage{enumitem}
%\usepackage{tabularx}

\urlstyle{tt}
\hypersetup{
    colorlinks,
    linkcolor={red!70!black},
    citecolor={blue!70!black},
    urlcolor={magenta!70!black}
}

\renewcommand{\bibname}{References}
\renewcommand{\contentsname}{Table of Contents}


\begin{document}

\newcommand*{\BuildingFromMainFile}{}

\subfile{chapters/intro_dept.tex}

\pagenumbering{roman}



\setcounter{tocdepth}{1}
\hypersetup{linkcolor=black}
\tableofcontents
\addcontentsline{toc}{chapter}{Table of Contents}
\newpage

\listoffigures 
\addcontentsline{toc}{chapter}{List of Figures}
\newpage

\listoftables 
\addcontentsline{toc}{chapter}{List of Tables}
\newpage

\thispagestyle{plain}
\section*{\centering{\Large{Abstract}}}
\addcontentsline{toc}{chapter}{Abstract}

\hypersetup{linkcolor={red!70!black}}

English abstract

\newpage

\thispagestyle{plain}
\section*{\centering{\Large{Zusammenfassung}}}
\addcontentsline{toc}{chapter}{Zusammenfassung}

Deutsch abstract

\newpage

\pagenumbering{arabic}


% paper 1 as chapter 2

\chapter[Feasibility of the bovine genome graphs]{\Large{Variant genotyping using local variation graphs}}
\label{chap:locgraph}
\subsection*{Preface: Bridging text between Chapter 1 and Chapter 2}

\normalsize
This chapter assessed the feasibility of the genome graphs in cattle genome for variant genotyping; the first graph-based genotyping approach applied in any agricultural animal. The region-specific graphs were constructed using variations discovered from the sequencing cohort implemented using \emph{Graphtyper}. The genotyping pipeline was based on refined sequencing read alignment towards the local graphs. The genotyping analysis showed that graph-based approach using \textit{Graphtyper} is highly accurate, outperforming state-of-the-art methods based on linear reference e.g., \textit{SAMtools, \emph{GATK}}. \\

\bigskip

% I assessed \emph{Graphtyper} software for variant genotyping in cattle.
% \emph{Graphtyper} performed two round of genotyping. The first is to discover variants from linear
% genome. And the second round used the variants discovered in the first round to construct a local genome graph and used it to refine the genotypes. I discovered that \textit{graph genotyping} using \textit{Graphtyper} is highly accurate in cattle and outperform current approaches e.g., \textit{SAMtools, \emph{GATK}} that are based on linear reference. My work is the first to apply \textit{graph genome} for sequence variant genotyping in the livestock genome.  I implemented the graph genotyping pipeline and it is now publicly available at \\  
% \url{https://github.com/danangcrysnanto/Graph-genotyping-paper-pipelines}. \\ 

\emph{Contribution}: Hubert Pausch and I conceived the study. Christine Wurmser generated the sequencing data. I wrote the graph genotyping pipelines and Hubert Pausch and I performed the analyses. Hubert Pausch and I wrote the manuscript. 

\onehalfspacing
\include{chapters/chapter2}

% paper 2 as chapter 3

\chapter[Bovine whole-genome variations graphs]{\Large{Analysis of the bovine whole-genome variation graphs}}
\label{chap:wholegraph}

\subsection*{Preface: Bridging text between Chapter 2 and Chapter 3}
\normalsize
This chapter developed a variation graphs pipeline using \emph{vg toolkit} that augmented external variations and enabling analyses on full genome-scale. The first cattle whole-genome graph was constructed using the pipeline; the first assessment of the gigabase genome-graph on the species other than human. The application of this whole-genome graph facilitated accurate read mapping and unbiased sequence variant genotyping. \\

\bigskip

\emph{Contribution}: Hubert Pausch and I conceived the study, I wrote the whole-genome graph pipelines and Hubert Pausch and I performed analyses. Hubert Pausch and I wrote the manuscript. 

% In this chapter, I constructed the first cattle whole genome graph and performed the first assessment of the gigabase genome graph on the species other than human. I showed using both real and simulated datasets that the graph facilitate accurate read mapping and unbiased sequence variant genotyping. I developed the graph pipeline further from previous implementation based on \emph{vg toolkit} allowing graph analysis performed in a full genome scale. Additionally, I included catalogues of previously discovered variants to the graph, which showed that \emph{breed-specific} graph perform similarly as the \emph{multi-breed pangenome graph}. \\

% \emph{Contribution}: I and Hubert Pausch conceived the study, I wrote the full genome graph pipelines and performed all analyses. I wrote the initial draft of the manuscript with input from Hubert Pausch. 

\onehalfspacing
\include{chapters/chapter3}

\chapter[Bovine multi-assembly graphs]{\Large{Analysis of the bovine multi-assembly graphs}}
\label{chap:multigraph}

\subsection*{Preface: Bridging text between Chapter 3 and Chapter 4}

\normalsize
This chapter explored the utility of multi-assembly graphs that integrated the collection of genome assemblies into a unified representation using \emph{minigraph}. The first bovine multi-assembly graph was constructed that unified six cattle assemblies, including its close relatives of Brahman and Yak. The application of the multi-assembly graph identified the 70 Mb sequences not included in the existing \emph{Bos taurus} reference genome. Further analysis showed that these non-reference sequences contain abundant functionally relevant sequences. \\

\bigskip


\emph{Contribution}: Hubert Pausch and I conceived the study. Zih-Hua Fang coordinated the sampling and long-read sequencing. Alexander Leonard assembled the Original Braunvieh genome. Hubert Pausch, Alexander Leonard, and I performed the analyses and wrote the manuscript. 

\onehalfspacing
\include{chapters/chapter4}

% Appendixes 

\chapter*{\centering{Supplementary Materials \\ Chapter \ref{chap:locgraph}}}
\addcontentsline{toc}{chapter}{Supplementary Materials Chapter \ref{chap:locgraph}}
\singlespacing
\fancyhead[C]{APPENDICES}
\include{chapters/supp_chap2}

\chapter*{\centering{Supplementary Materials \\ Chapter \ref{chap:wholegraph}}}
\addcontentsline{toc}{chapter}{Supplementary Materials Chapter 3}
\singlespacing
\fancyhead[C]{APPENDICES}
\include{chapters/supp_chap3}

\chapter*{\centering{Supplementary Materials \\ Chapter \ref{chap:multigraph}}}
\addcontentsline{toc}{chapter}{Supplementary Materials Chapter 4}
\singlespacing
\fancyhead[C]{APPENDICES}
\include{chapters/supp_chap4}

\end{document}
