\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

% \usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}%\centering
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]


\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumetalk}[4]{\small{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
    }
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}



\begin{center}
    {\LARGE \textbf{Danang Crysnanto}} \\ \vspace{2pt}
    \begin{multicols}{2}
    \begin{flushleft}
    Hoffeld 24 8057 Zurich\\
    \href{mailto:{danangcrysnanto@gmail.com}}{danangcrysnanto@gmail.com}
    \end{flushleft}
    
    \begin{flushright}
    \href{{https://github.com/danangcrysnanto}}{github.com/danangcrysnanto}\\
    \href{{https://www.linkedin.com/in/danangcrysnanto/}}{linkedin.com/danangcrysnanto}\\
    \end{flushright}
    \end{multicols}
\end{center}


%-----------EDUCATION-----------
\vspace{-2pt}
\section{Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {ETH Zurich}{Dec 2017 -- Present}
      {Doctoral in Animal Genomics}{Zurich, Switzerland}
      \resumeSubheading
      {The University of Edinburgh}{Aug 2016 -- Aug 2017}
      {Msc in Quantitative Genetics and Genome Analysis with \textbf{Distinction}}{Edinburgh, UK}
      \resumeSubheading
      {Bandung Institute of Technology}{Oct 2010 -- Oct 2014}
      {Bsc in Biology (Genetics) with \textbf{Cum Laude}}{Bandung, Indonesia}

  \resumeSubHeadingListEnd

\vspace{0.5 cm}

%%-----------EXPERIENCE-----------
%\section{Experience}
%  \resumeSubHeadingListStart
%    \resumeSubheading
%      {Ph.D. Researcher}{Sep. 2019 -- Present}
%      {Laser beams shooting research}{Molvanîa, Mv}
%      \resumeItemListStart
%        \resumeItem{Laser beams}
%        \resumeItem{Laser cooling techniques}
%        \resumeItem{Off blast!}
%    \resumeItemListEnd
%
%  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
 \textit{First-author publications}
 \begin{enumerate}[leftmargin=0.3in]
    \small{\item{\textbf{Crysnanto D.}, A. S. Leonard, Z. H. Fang, and H. Pausch, 2021. Novel functional sequences uncovered through a bovine multi-assembly graph. Accepted \textit{Proceedings of the National Academy of Sciences USA}
    \item{\textbf{Crysnanto D.}, and H. Pausch, 2020. Bovine breed-specific augmented reference graphs facilitate accurate sequence read mapping and unbiased variant discovery. \textit{Genome Biology}. 21:184}
    \item{\textbf{Crysnanto D.}, C. Wurmser, and H. Pausch, 2019. Accurate sequence variant genotyping in cattle using variation-aware genome graphs. \textit{Genetics Selection Evolution} 51:21 }
    \item{\textbf{Crysnanto D.}, and D. J. Obbard, 2019 Widespread gene duplication and adaptive evolution in the RNA interference pathways of the \emph{Drosophila obscura} group. \textit{BMC Evolutionary Biology} 19:1}
    
}}
 \end{enumerate}
  \textit{Co-author publications}

\begin{enumerate}[leftmargin=0.3in]
    \setcounter{enumi}{4}

    \small{

    \item{Nosková A., M. Bhati, N. K. Kadri, and \textbf{D. Crysnanto} et al., 2021 Characterization of a haplotype-reference panel for genotyping by low-pass sequencing in Swiss Large White pigs. \emph{BMC Genomics} 1–30}
      
    \item{Nosková A., C. Wurmser, \textbf{D. Crysnanto}, A. Sironen, P. Uimari, et al., 2020 Deletion of porcine BOLL is associated with defective acrosomes and subfertility in Yorkshire boars. \textit{Animal Genetics} 51: 945–949}
    
    \item{Fang Z. H., A. Nosková, \textbf{D. Crysnanto}, S. Neuenschwander, P. Vögeli, et al., 2020 A 63-bp insertion in exon 2 of the porcine KIF21A gene is associated with arthrogryposis multiplex congenita. \textit{Animal Genetics} 51: 820–823}
    
    \item{Hiltpold M., G. Niu, N. K. Kadri, \textbf{D. Crysnanto}, Z. H. Fang, et al., 2020 Activation of cryptic splicing in bovine WDR19 is associated with reduced semen quality and male fertility. \textit{PLoS Genetics}. 16: 1–27}
    
    \item{Bhati M., N. K. Kadri, \textbf{D. Crysnanto}, and H. Pausch, 2020 Assessing genomic diversity and signatures of selection in Original Braunvieh cattle using whole-genome sequencing data. \emph{BMC Genomics} 21(1)} 

}

\end{enumerate}

\section{Invited Talks}
% \textbf{Plant and Animal Genome Conference (PAG)}} \\ 01/2020 \textit{San Diego USA}
   
 \resumeSubHeadingListStart
%\textit{Conferences}
%\vspace{0.5 cm}
 \small{
 
    \resumetalk {CIGENE Seminar Series}{March 2021}
      {Talk title: Bovine pangenomics}{NMBU Norway}
      \resumetalk {International Virtual Animal Breeding Journal Club}{Sept 2020}
      {Talk title: Bovine pangenomics}{USDA USA}
   \resumetalk {Plant and Animal Genome Conference (PAG)}{Jan 2020}
      {Talk title: Bovine pangenome graph enables unbiased genetic variants discovery}{San Diego USA}
      
  \resumetalk {Livestock Genomics session - Genome Informatics}{Sept 2018}
     {Talk title: Development of graph-based genotyping pipelines for bovine whole-genome data}{Cambridge UK}
     
    \resumetalk {Population Genetics (PopGroup) Conference }{Jan 2018}
     {Talk title: Widespread gene duplications in \textit{Drosophila} immune system pathways}{Oxford UK}
     
      
    }
\resumeSubHeadingListEnd
    
\section{Awards}
% \textbf{Plant and Animal Genome Conference (PAG)}} \\ 01/2020 \textit{San Diego USA}
   
 \resumeSubHeadingListStart
%\textit{Conferences}
%\vspace{0.5 cm}
 \small{
 
    \resumetalk {Sir Kenneth Mather Memorial Prize}{Jan 2018}
      {Annual award for a MSc or PhD student of any UK University or Research Institutions \\ which shown an outstanding performance in the area of quantitative and population genetics. }{The Genetics Society}
    \resumetalk {The Douglas Falcone Prize }{Oct 2017}
      {Annual award for the best master’s thesis in Quantitative Genetics and Genome Analysis}{The University of Edinburgh}
   \resumetalk {Bronze Medalist 21st International Biology Olympiad}{Aug 2010}
      {Winning a medal on a highly prestigious International bioscience Olympiad}{International Biology Olympiad}
     
      
    }
\resumeSubHeadingListEnd


%\textit{Group meeting}

%-----------PROGRAMMING SKILLS-----------
%\section{Technical Skills, Language Skills, and Interests}
% \begin{itemize}[leftmargin=0.15in, label={}]
%    \small{\item{
%     \textbf{Programming Languages}{: Python, R, Linux/Unix} \\
%     \textbf{Data Science}{: R Tidyverse, Python Data Science (Numpy, Pandas, Jupyter)}\\
%     \textbf{Interactive data visualization}{: Shiny, Flask} \\
%     \textbf{Computational pipelines}{: Snakemake } \\
%     \textbf{Reproducible data analysis}{: Git, Docker} \\
%     \textbf{Others}{: Affinity Designer, Microsoft Office, \LaTeX, vim, vscode} \\
%     \textbf{Languages}{: Indonesian (native), German (A2), English} \\
%     \textbf{Interests}{: Landscape Photography}
%     
%    }}
% \end{itemize}

%%-----------CERTIFICATIONS-----------
%\section{Extracurricular}
% \begin{itemize}[leftmargin=0.15in, label={}]
%    \small{\item{
%     \textbf{Specialization}{:\href{certification site}{ Course} } 
%    }}
%    
% \end{itemize}
%
\end{document}
